A primer to numerical simulations: The perihelion motion of Mercury

### 2017-12-07 tex/MercuryNumerical.tex
Inka-> +Citations and removed tasks

\usepackage[utf8]{inputenc}         % this is needed for Umlaute
\usepackage[english,ngerman]{babel} % this is needed for Umlaute
\usepackage[T1]{fontenc}            % this is needed for correct output of umlauts in pdf

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tasks}\label{sec:tasks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{@IH: this could be a little bit more verbose. Maybe include in section below.}
Ideas for questions:
\begin{itemize}
	\item Mass and motion of sun
	\item Estimate \texttt{dt} and also \texttt{T} in order to cover roughly two "mercury years".
	\item What does happen when you change those units?
	\item Compare values to the values in \cite{}.  Where does the difference come from?
	\item Start with $\alpha=0$. What do you observe?
\end{itemize}

@@

Of course by optimizing the code, an improvement in accuracy can be achieved without changing $\Delta t$.
The simplest way to demonstrate this might be given by the implementation of the Verlet\cite{}\todo{@IH: cite Verlet} integration instead of using the simple Euler method.
\end{itemize}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bib
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{alphadin}
%\bibliography{MercuryNumerical}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage[utf8]{inputenc}         % this is needed for Umlaute
\usepackage[english,ngerman]{babel} % this is needed for Umlaute
\usepackage[T1]{fontenc}            % this is needed for correct output of umlauts in pdf
\usepackage{cite}

@@

@@

Of course by optimizing the code, an improvement in accuracy can be achieved without changing $\Delta t$.
The simplest way to demonstrate this might be given by the implementation of the Verlet (see e.g.~\cite{Hairer03geometricnumerical} and references therein) integration instead of using the simple Euler method.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{alphadin}
\bibliography{References}

@@
